---
title: "ODISSEI code library"
author: 
  name: "ODISSEI FAIR support team "
  email: "fairsupport@odissei-data.nl"
  affiliation: "Erasmus University Rotterdam - ODISSEI"
date: '`r Sys.Date()`'
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = "UTF-8", output_file="test.html") })
output: 
  html_document:
    theme: cosmo
    toc: yes
    toc_float:
      collapsed: false
    css: docs.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
suppressWarnings(library(DT))
suppressWarnings(library(tidyverse))
suppressWarnings(library(stringr))
```


# Welcome
The ODISSEI code library contains a collection of scripts detailing data processing and analysis steps of projects using LISS panel data and CBS (Statistics Netherlands) microdata. Some of the projects receive funding via [ODISSEI](https://odissei-data.nl/en/).

If you have comments, reach out to the [ODISSEI FAIR support team](mailto:fairsupport@odissei-data.nl).

Do you want to submit your own project and code to be added to the library? Please submit an issue using the Submission code issue template on the [GitHub repository](https://github.com/odissei-data/ODISSEI-code-library) or send an email to the [ODISSEI FAIR support team](mailto:fairsupport@odissei-data.nl).

# Code libraries
## CBS microdata 
```{r loaddataCBS}
getwd()
df = read.csv("~/GitHub/odissei/ODISSEI-code-library/_data/cbs.csv", encoding = "UTF-8", check.names=FALSE)
colnames(df)[1] = c("X")
df = df |> dplyr:::select(-c("X")) 
DT::datatable(df, escape = FALSE,
              filter = "top", 
              options = list(dom = "ft", 
                            pageLength = 1000, 
                            autoWidth = TRUE),
              rownames = FALSE)
```

## LISS panel
```{r loaddataLISS}
df2 = read.csv("~/GitHub/odissei/ODISSEI-code-library/_data/liss.csv", encoding = "UTF-8", check.names=FALSE)
colnames(df2)[1] = c("X")
df2 = df2 |> dplyr:::select(-c("X")) 
DT::datatable(df2, escape = FALSE,
              filter = "top", 
              options = list(dom = "ft", 
                            pageLength = 1000, 
                            autoWidth = TRUE),
              rownames = FALSE)
```